---
title: "Dominance-diversity trade-off"
author: "Julie Sheard"
date: "28/1/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description

This script is for the analysis of the dominance-diversity trade-off/the Impoverishment rule for ants across a latitudinal gradient. Expected trade-off is that diversity decreases as dominance increases or that diversity intially increases and then decreases as dominance increases.

# Setting up

## Clear R's brain
```{r}
rm(list=ls()) #Clear R's brain
ls() #List objects in R's brain
```

## Load packages
```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(jtools)
library(lme4)
library(cowplot)
library(car)
```

## Load and check data
```{r}
SITES<-read.csv("H:/Documents/Projects/Latitude/data/site measures_03042020.csv", sep=";") #Load site-level data. 38 sites

str(SITES) #Check data is correct
```

# Check for random effects

## Test whether a random effect (geographic or environmental variables) should be included

```{r}
mod1 <- lm(Species~Dominant.species, data = SITES)
mod2 <- lmer(Species~Dominant.species + (1|Locality), data = SITES, REML=FALSE)
mod3 <- lmer(Species~Dominant.species + (1|NDVI), data = SITES, REML=FALSE)
mod4 <- lmer(Species~Dominant.species + (1|bio1), data = SITES, REML=FALSE)
mod5 <- lmer(Species~Dominant.species + (1|bio12), data = SITES, REML=FALSE)
mod6 <- lmer(Species~Dominant.species + (1|AET), data = SITES, REML=FALSE)

anova(mod2, mod1) # p = 0.02 *
anova(mod3, mod1) # p = 0.54
anova(mod4, mod1) # p = 0.133
anova(mod5, mod1) # p = 0.14
anova(mod6, mod1) # p = 0.14
```

There is a significant effect of including the random factor 'Locality', which is in line with our expectation that there will be spatial autocorrelation in the data. 

# Test the dominance-diversity trade-off

## Does the number of dominant species affect overall species richness? 

Fit linear mixed effects model
Test whether the number of dominant species affects the overall number of species at a site. The assumption is that as the richness of dominant species increases, the overal number of species decreases.  

```{r}
#Linear model for the effect of dominant species number
sites_linear<-lmer(Species~Dominant.species + (1|Locality), data = SITES, REML=FALSE)
summary(sites_linear)
summ(sites_linear)
#Polynomial model for the effect of dominant species number
sites_non<-lmer(Species~poly(Dominant.species,2)+(1|Locality), data=SITES, REML=FALSE)
summary(sites_non)
summ(sites_non)

anova(sites_linear, sites_non)
```

There is a significant linear relationship between species richness and the number of dominant species. 

```{r}
#Linear model for the effect of relative worker numbers of dominants on species diversity

wn_lin <-lmer(Species~Dominant.abundance.prop + (1|Locality), data = SITES, REML=FALSE)
summary(wn_lin)
summ(wn_lin)
#Polynomial model for the effect of relative worker number of dominants
wn_poly<-lmer(Species~poly(Dominant.abundance.prop,2)+(1|Locality), data=SITES, REML=FALSE)
summary(wn_poly)
summ(wn_poly)

#Model comparison
anova(sites_linear, sites_non)
```

### Plot the relationships
```{r}
#Effect of dominant species number
(Site_sp<- ggplot(aes(y=Species, x=Dominant.species), data = SITES)+
    geom_point(size=3, shape=16) + 
    geom_smooth(method = "lm", se=F, colour="black", size = 1) +
    theme_classic() + 
    xlab("Number of dominant ant species at sites") +
    ylab("Species richness at site") +
    scale_y_continuous(breaks = seq(0, 14, by = 2))+
    theme(panel.grid.major = element_blank(),  panel.grid.minor = element_blank(),
         axis.text    = element_text(face = "bold", size=12),
         axis.title = element_text(size=12),
         legend.title = element_blank()))

#Effect of dominant species worker proportion
(Site_abs<- ggplot(aes(y=Species, x=Dominant.abundance.prop), data = SITES)+ 
    geom_point(size=3, shape=16) + 
    geom_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1, se=F, colour="black") +
    theme_classic() + 
    xlab("Relative worker number of dominants") +
    ylab("") +
    scale_y_continuous(breaks = seq(0, 14, by = 2))+
    scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
    theme(panel.grid.major = element_blank(),  panel.grid.minor = element_blank(),
         axis.text    = element_text(face = "bold", size=12),
         plot.margin = margin(10, 20, 10, 10),
         axis.title = element_text(size=12),
         legend.title = element_blank()))
```

### Create figure with both plots
```{r}
plot_grid(Site_sp, Site_abs, ncol=2, align="hv", labels = c("a)", "b)"), hjust=0.1, vjust=1)
```
