---
title: "Mixed models"
author: "Julie Sheard"
date: "1/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description

This script is for the analysis of the dominance-discovery trade-off, the dominance-temperature range trade-off and the dominance-resource generalism trade-off for ants across a latitudinal gradient. Expected trade-off is that dominance decreases with increasing discovery ability, decreases with increasing temperature tolerance and decreases with increasing resource generalism.

# Setting up

## Clear R's brain
```{r}
rm(list=ls()) #Clear R's brain
ls() #List objects in R's brain
```

##Trade-offs with dominance

```{r}
#Load data
DOM <-read.csv("H:/Documents/Projects/Latitude/data/dominance measures_22012020.csv", sep=";")
str(DOM) #Check data is correct 
```

Dominance is measured as the monopolization percentage
Discovery is measured as the percentage of baits discovered where the species was first to arrive

### Find best probability distribution

```{r}
library(car)
library(MASS)
library(lme4)
library(ggplot2)

DOM$Mono.found.t <- DOM$Mono.found*100
DOM$Mono.found.t1 <- round(DOM$Mono.found.t) +1

#Test for normality
shapiro.test(DOM$Mono.found)
```

Data is not normal, p < 0.05


#Find best model fit

```{r}
qqp(DOM$Mono.found.t, "norm") #Normal distribution
qqp(DOM$Mono.found.t, "lnorm") #log-normal distribution

nbinom <- fitdistr(DOM$Mono.found.t1, "Negative Binomial")
qqp(DOM$Mono.found.t1, "nbinom", size = nbinom$estimate[[1]], mu = nbinom$estimate[[2]]) #Negative binomial

gamma <- fitdistr(DOM$Mono.found.t1, "gamma")
qqp(DOM$Mono.found.t1, "gamma", shape = gamma$estimate[[1]], rate = gamma$estimate[[2]]) #Gamma distribution

fitp<-fitdistr(DOM$Mono.found.t1, "Poisson")
qqp(DOM$Mono.found.t1, "pois", fitp$estimate) #Poisson distribution

```

Since our dependent variable (monopolization of baits found) is non-normal we use GLMM to test for an association between the two variables. 

#Laplace approximation <- this is the one I used
```{r}
library(mlmRev)

GHQ <- glmer(Mono.found ~ First.percent + Temp.range + PIE + (1 | Locality), data = DOM,
    family = binomial(link = "logit"), nAGQ = 25)  # Set nAGQ to # of desired iterations

summary(GHQ)

car::vif(GHQ)
```

#Diffference between dominant and subordinate species in means
```{r}
t.test(First.percent~Type, data = DOM)
t.test(Temp.range~Type, data = DOM)
t.test(PIE~Type, data = DOM)

```

#Trade-off drivers
```{r}
#Load r values calculated above
relation <-read.csv("H:/Documents/Projects/Latitude/data/MANOVA_02042020.csv", sep=";")
```

#Test for normality
```{r}
#Test for normality
shapiro.test(relation$rho..MonoFirst.)
shapiro.test(relation$rho..MonoTRange.)
shapiro.test(relation$rho..MonoPIE.)
```
#Find best model fit

```{r}
qqp(relation$rho..MonoFirst.t, "norm") #Normal distribution
qqp(relation$rho..MonoTRange.) #Normal distribution
qqp(relation$rho..MonoPIE.t, "norm") #Normal distribution

```

Data is normally distributed

#Model effect of climate on Dominance-Discovery trade-off
```{r}
lmm <- lmer(rho..MonoFirst. ~ bio1+bio12+AET+I(NDVI_1km_monthly*100) + (1 | Locality), data = relation,
    REML = FALSE)
summary(lmm)

#NDVI was rescaled for modelling purposes 

Anova(lmm)

car::vif(lmm)

#Remove AET
lmm2 <- lmer(rho..MonoFirst. ~ bio1+bio12+I(NDVI_1km_monthly*100) + (1 | Locality), data = relation,
    REML = FALSE)
summary(lmm2)

car::vif(lmm2)

p.adjust(0.12, method="bonferroni", n=4)

```


#Model effect of climate on Dominance-thermal tolerance trade-off
```{r}
lmm <- lmer(rho..MonoTRange. ~ bio1+bio12+AET+I(NDVI_1km_monthly*100) + (1 | Locality), data = relation,
    REML = FALSE)
summary(lmm)

#NDVI was rescaled for modelling purposes 
Anova(lmm)

car::vif(lmm)

#Remove AET
lmm2 <- lmer(rho..MonoTRange. ~ bio1+bio12+I(NDVI_1km_monthly*100) + (1 | Locality), data = relation,
    REML = FALSE)
summary(lmm2)
Anova(lmm2)

car::vif(lmm2)

p.adjust(0.24, method="bonferroni", n=4)

```


#Model effect of climate on Dominance-resource generalism tolerance trade-off
```{r}
lmm <- lmer(rho..MonoPIE. ~ bio1+bio12+AET+I(NDVI_1km_monthly*100) + (1 | Locality), data = relation,
    REML = FALSE)
summary(lmm)

#NDVI was rescaled for modelling purposes 
Anova(lmm)

car::vif(lmm)

#Remove AET
lmm2 <- lmer(rho..MonoPIE. ~ bio1+bio12+I(NDVI_1km_monthly*100) + (1 | Locality), data = relation,
    REML = FALSE)
summary(lmm2)
Anova(lmm2)

car::vif(lmm2)

p.adjust(0.02, method="bonferroni", n=3)

```

#Plot effect of Annual precipitation (bio12) on the dominance-resource generalism trade-off

```{r}
(g<- ggplot(aes(y=rho..MonoPIE., x=bio12), data = relation)+ 
   geom_point() +
   theme_bw() + 
   ylab("Dominance-resouce generalism trade-off") +
   xlab("Annual precipitation") +
   theme(axis.text    = element_text(face = "bold"),
         legend.title = element_blank())  )
```

#Redo analysis with outlier removed
```{r}
sub_rel <- relation[-c(7),] 

lmm <- lmer(rho..MonoPIE. ~ bio1+bio12+AET+I(NDVI_1km_monthly*100) + (1 | Locality), data = sub_rel,
    REML = FALSE)
summary(lmm)

Anova(lmm)

p.adjust(0.052, method="bonferroni", n=3)

```


